An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-24 VLDB2026/main.tex
1

		\multicolumn{2}{|c|}{\textbf{Characteristics/Algorithms}} & \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS} & \textbf{ACORN} & \textbf{UNG} & \textbf{Puck} & \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{Win}
		 \\ \hline
		\multirow{6}{*}{\textbf{AF}} 
		& Filter Type         & C   & C   & C   & C   & B   & B   & B   & \multicolumn{5}{c|}{} \\ \cline{2-9}
		& AND                 & Y   & N   & N   & Y   & Y   & Y   & Y   & \multicolumn{5}{c|}{\multirow{4}{*}{\centering\shortstack{AF\\not support}}} \\ \cline{2-9}
		& OR                  & N   & Y   & Y   & N   & Y   & Y   & Y   & \multicolumn{5}{c|}{} \\ \cline{2-9}
		& Flexible Attributes & N   & Y   & Y   & Y   & Y   & Y   & Y   & \multicolumn{5}{c|}{} \\ \cline{2-9}
		& Complex Boolean     & N   & N   & N   & N   & Y   & N   & N   & \multicolumn{5}{c|}{} \\ \hline

@@

		\centering
		%	 \setlength{\abovecaptionskip}{0cm}
		%	\setlength{\belowcaptionskip}{0.1cm}
		\footnotesize{
			\begin{minipage}{\linewidth}
				\vspace{0.1cm}
				\textsuperscript{A} Post-filtering, 
				\textsuperscript{B} Pre-filtering, 
				\textsuperscript{C} Simultaneous filtering, 
				\textsuperscript{Y} Support, 
				\textsuperscript{N} Unsupport. 
				\textit{AND} and \textit{OR} indicate whether the algorithm supports the corresponding logical operations.
				\textit{Flexible Attributes} indicates whether the number of query attributes can differ from the number of attributes used during index construction. 
				\textit{Complex Boolean} indicates if the algorithm supports complex expressions, such as using the NOT operator or nested logic with parentheses.
				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
				\textit{Disk Support} indicates whether the algorithm supports disk storage.
				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm.
		\end{minipage}}

@@

		\includegraphics[width=0.95\textwidth]{figures/exp/exp_3_1.pdf}
		\caption{Effect of attribute distribution on query performance (single thread)}
		\label{fig:exp_3_1}

		\footnotesize{
		\begin{center}
			\begin{minipage}{\linewidth}
				\centering	
				\textit{Strong} : robust to attribute distribution shifts,  \textit{Weak} : sensitive to attribute distribution shifts
			\end{minipage}
		\end{center}
		}
	\end{figure*}

	\textit{\textbf{Multi-Attribute Building and Multi-Attribute Query.}}  
	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world scenarios. To evaluate algorithm performance under this setting, we construct the index using 3 uniformly distributed attributes and apply filtering on all 3 attributes simultaneously during queries. \textcolor{orange}{In this experiment, we only evaluate the algorithms that support this query scenario.}
	%	\textcolor{red}{As Filtered-DiskANN does not support the AND rule used in our multi-attribute queries, it is excluded.}
	%	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world application scenarios. To evaluate algorithm performance under such scenario, we construct the index using 3 uniformly distributed attributes and apply filtering conditions on all 3 attributes simultaneously during the query process.

@@

@@

	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}} 
%	\textcolor{cyan}{To investigate the impact of different server configurations on the performance of the algorithms, we conducted additional experiments on Server B using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}. Compared with the experimental results on Server A shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}f, the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations. Due to the lower CPU frequency and smaller RAM capacity of Server B compared to Server A, the QPS values are slightly lower across all methods.}
	\textcolor{red}{To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}. Compared with the experimental results on the original server (as shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}(f)), the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations. Due to the lower CPU frequency and smaller RAM capacity, the QPS values are slightly lower across all methods.}

@@

		\hspace*{5pt}
		% 放大的图例（占满单栏）
		\includegraphics[width=0.98\columnwidth]{figures/exp/attribute_legend.pdf}

		%\vspace{0.1cm}
		\begin{subfigure}[t]{0.98\columnwidth}
		\centering
		% First plot for the shared subfigure
		\includegraphics[width=0.507\linewidth]{figures/exp/attribute_multimodel.pdf}
		\hfill % Pushes the two plots apart
		% Second plot for the shared subfigure
		\includegraphics[width=0.48\linewidth]{figures/exp/attribute_multimodel_1.pdf}

		% Shared caption for the two plots above
		\captionsetup{font=small}
		\caption{MultiModal}
		\label{fig:MultiModal} % A single label for the combined subfigure
		\end{subfigure}

		\begin{subfigure}[t]{0.507\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/exp/attribute_85.pdf}
			\caption{\footnotesize Different Computer}
			\label{fig:Different Computer}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.48\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/exp/attribute_100M.pdf}
			\caption{\footnotesize Big Dataset}
			\label{fig:Big Dataset}
		\end{subfigure}

		\caption{\textcolor{violet}TrinityExtension——Attribution}
		\label{fig:TrinityExtension——Attribution}
	\end{figure}

@@

		\hspace*{5pt}
		% 放大的图例（占满单栏）
		\includegraphics[width=0.98\columnwidth]{figures/indexData/rangeFilter_legend_only.pdf}

		%\vspace{0.1cm}

		% 三图横排
		\begin{subfigure}[t]{0.495\columnwidth}
			\centering
			\captionsetup{font=small}
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_build_time_comparison_query.pdf}
			\caption{\footnotesize Construction time}
			\label{fig:rangeFilter_build_time}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.495\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf}
			\caption{\footnotesize Index size}
			\label{fig:rangeFilter_index_size_mb}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.495\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_memory_mb_comparison_query.pdf}
			\caption{\footnotesize Build peak memory}
			\label{fig:rangeFilter_build_memory_mb}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.495\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/searchMem/range_memory_comparison.pdf}
			\caption{\footnotesize Search peak memory}
			\label{fig:rangeFilter_search_memory_mb}
		\end{subfigure}

		%		\caption{Time and space overhead of range filtering index construction}
%		\caption{Time and space overhead of index construction}
		\caption{\textcolor{violet}{Time and space overhead}}
		\label{fig:rangeFilter_build_index_comparison}
	\end{figure}

	%Similar to the evaluation of \textit{Attribute Filtering} algorithms, 
	Similarly, we also evaluate \textcolor{orange}{4} key metrics mentioned above in \textit{Range Filtering} algorithms. 
%	\textcolor{orange}{For the YT-Audio dataset with synthetic attributes and the YT-Audio dataset with real attributes, we can found that the data for index construction is basically the same, indicating that the authenticity of the attribute has almost no effect on index construction.However, the WIT dataset with synthetic labels is 2048-dimensional, while the WIT-Real dataset with real labels is 512-dimensional, so the dimension will cause a big difference.}

@@

	\textcolor{orange}{Note: For large-scale datasets, all algorithms are built using 64 threads for efficiency, except DSG, which only supports single-threaded construction. As a result, DSG takes significantly longer to build on Deep100M.
	}

	\textit{\textbf{Index size.}} 
	As shown in Figure~\ref{fig:rangeFilter_index_size_mb}, Among all algorithms, Faiss has the smallest index size. Because IVF only adds centroid data and partition information to the vector dataset, the IVF index is only slightly larger than the vector dataset.
	%On low-dimensional datasets (Deep, YT-Audio), 
	PASE requires the most storage. Its implementation likely wastes space due to alignment padding and inefficient encoding. %(e.g., Base64).
	\textcolor{orange}{DSG is an improvement over SeRF. Compared to SeRF, DSG stores additional information for each edge in its index structure, resulting in a significant increase in index size on large-scale datasets.
	}

	%SeRF maintains a compact index for low-dimensional data. However, for high-dimensional dataset (WIT), SeRF stores more edges and dynamic range data, significantly increasing its size.

	\textit{\textbf{Build peak memory.}}
	\textcolor{orange}{As explained in the build peak memory analysis for attribute filtering, the build peak memory depends on the sum of the index size and the dataset size, as shown in Figure~\ref{fig:rangeFilter_build_memory_mb}. Range filtering also follows this pattern. The reason why PASE deviates from this trend has been discussed earlier, and is not repeated here to save space.}

%	As Figure~\ref{fig:rangeFilter_build_memory_mb} shows, Faiss uses the least memory on low-dimensional datasets. It stores minimal temporary data during index construction.
%	
%	On low-dimensional datasets, DSG and WinFilter exhibit higher peak memory usage compared to other algorithms. This suggests that their index structures suffer from severe structural redundancy and are difficult to compress in low-dimensional scenarios.
%	
%	For high-dimensional dataset WIT, iRange achieves the lowest peak memory usage. It pre-builds graphs only for a limited number of intervals, avoiding explicit index construction for all possible query ranges. Its index structure remains stable in high dimensions without significant graph growth. This effectively controls index size, making iRange more advantageous for high-dimensional datasets.
%	In contrast, \textcolor{orange}{Milvus exhibits the highest memory consumption,}

		\textit{\textbf{\textcolor{orange}{Search peak memory.}}}
		\textcolor{orange}{As for the search peak memory usage, we can find from the Figure ~\ref{fig:rangeFilter_search_memory_mb} that it is basically consistent with the build peak memory usage trend. As we analyzed in the section on attribute filtering.
		}

@@

	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}}
	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:Different_Computer_range}. When compared with the experimental results of the original server shown in Figure~\ref{fig:exp_8_2}a, our findings remain consistent with those reported in Section 4.2.4. For brevity and due to space limitations, we omit further discussion of these redundant results.}
%	\textcolor{cyan}{Consistent with Section 4.2.4, we conducted additional range filtering experiments using the YT-Audio-Real dataset on the same server, with results shown in Figure \ref{fig:Different Computer range}. Compared with the original server's experimental results (Figure \ref{fig:exp_8_2}($e$)), the conclusions remain identical to those described in Section 4.2.4. Due to space constraints, these details are not reiterated here.}

@@

\begin{table*}[htbp]
	\caption{Algorithm Recommendation}
	\resizebox{\textwidth}{!}{
		\begin{tabular}{|l|*{16}{c|}}
			\hline
			\multirow{2}{*}{\textbf{Application Scenarios / Algorithms}} 
			& \multicolumn{6}{c|}{\textbf{AF}} 
			& \multicolumn{5}{c|}{\textbf{RF}} 
			& \multicolumn{5}{c|}{\textbf{AF / RF}} \\
			\cline{2-17}
			& \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS}  & \textbf{UNG} & \textbf{Puck} 
			& \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{Win} 
			& \textbf{ACORN}& \textbf{Faiss} & \textbf{Milvus} & \textbf{VBASE} & \textbf{PASE} \\
			\hline
			\textbf{Query Performance} & H & M & H & M &\textbf{H} & H & M & M & L & M & H & M/M & M/M & M/M & L/L & L/L \\
			\textbf{Index Time} &M  &M  &M  &M  &M  &H  &L  &M  &H  &L  &L  &L/L &\textbf{H}/ \textbf{H} &M/H  &M/M  &L/L  \\
			\textbf{Peak Memory} &L  &M  &M  &M  &M  &H  &L  &L  &M  &L  &L  &L/L  &\textbf{H}/\textbf{H}  &M/M  &H/M  &H/H \\

			\textbf{Large-Scale Dataset} & H & H & L & L &\textbf{H} &H  &M  &H  &M  &H  &\textbf{H}  &M/L  &L/M  &L/L  &M/M  &-  \\
			\textbf{Rare Attribute \& Low Range} &M  &M  &H  &H &\textbf{H}  &H  &H  &H  &L  &M  &\textbf{H} &M/M  &M/M  &L/L  &L/L  &L/L  \\
			\textbf{Robust to MultiModal Dataset} &H  &H  &L  &H  &\textbf{H}  &L  &M  &H  &M  &H  &\textbf{H}  &H/H  &M/M  &L/L  &L/L  &-/-  \\
			\textbf{Robust to Attribute Distribution} &L  &L  &H  &H  &H  &H  &-  &-  &-  &-  &-  &H/-  &L/-  &\textbf{H}/-  &L/-  &L/-  \\
			\textbf{High LID Dataset} &H  &M  &H  &M  &\textbf{H}  &M  &M  &H  &M  &H  &\textbf{H}  &L/L  &M/H  &L/L  &L/M  &L/L  \\
			\textbf{General-Purpose} &\faCheck  &\faCheck  &\faTimes  &\faTimes  &\faCheck  &\faTimes  &\faTimes  &\faCheck &\faTimes  & \faTimes &\faCheck&\faTimes  &\faCheck  &\faCheck  &\faTimes &\faTimes  \\
			\hline
		\end{tabular}
	}
	\centering
\end{table*}

>>>>

		\multicolumn{2}{|c|}{\textbf{Characteristics/Algorithm}} & \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS} & \textbf{ACORN} & \textbf{UNG} & \textbf{Puck} & \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{Win}
		 \\ \hline
		\multirow{6}{*}{\textbf{AF}} 
		& Filter Type         & C   & C   & C   & C   & B   & B   & B   & \multicolumn{5}{c|}{} \\ \cline{2-9}
		& AND                 & Y   & N   & N   & Y   & Y   & Y   & Y   & \multicolumn{5}{c|}{\multirow{4}{*}{\centering\shortstack{AF\\not support}}} \\ \cline{2-9}
		& OR                  & N   & Y   & Y   & N   & Y   & Y   & Y   & \multicolumn{5}{c|}{} \\ \cline{2-9}
		& Flexible Attributes & N   & Y   & Y   & Y   & Y   & Y   & Y   & \multicolumn{5}{c|}{} \\ \cline{2-9}
		& Complex Boolean     & N   & N   & N   & N   & Y   & N   & N   & \multicolumn{5}{c|}{} \\ \hline

@@

		\centering
		%	 \setlength{\abovecaptionskip}{0cm}
		%	\setlength{\belowcaptionskip}{0.1cm}
		\footnotesize{
			\begin{minipage}{\linewidth}
				\vspace{0.1cm}
				Win: WinFilter, Filtered: Filtered-DiskANN, Stitched: StitchedVamana. 
				\textsuperscript{B} Pre-filtering, 
				\textsuperscript{C} Simultaneous filtering, 
				\textsuperscript{Y} Support, 
				\textsuperscript{N} Unsupport. 
				\textit{AND} and \textit{OR} indicate whether the algorithm supports the corresponding logical operations.
				\textit{Flexible Attributes} indicates whether the number of query attributes can differ from the number of attributes used during index construction. 
				\textit{Complex Boolean} indicates if the algorithm supports complex expressions, such as using the NOT operator or nested logic with parentheses.
				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
				\textit{Disk Support} indicates whether the algorithm supports disk storage.
				\textit{Base} indicates the foundational ANN algorithm for the hybrid query method.
		\end{minipage}}

@@

		\includegraphics[width=0.95\textwidth]{figures/exp/exp_3_1.pdf}
		\caption{Effect of attribute distribution on query performance (single thread)}
		\label{fig:exp_3_1}
	\end{figure*}

	\textit{\textbf{Multi-Attribute Building and Multi-Attribute Query.}}  
	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world scenarios. To evaluate algorithm performance under this setting, we construct the index using 3 uniformly distributed attributes and apply filtering on all 3 attributes simultaneously during queries. \textcolor{orange}{Note that FilterDiskANN only supports Boolean OR logic and does not support Boolean AND. Therefore, its two Vamana-based methods are excluded from the multi-attribute construction and search experiments.}
	%	\textcolor{red}{As Filtered-DiskANN does not support the AND rule used in our multi-attribute queries, it is excluded.}
	%	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world application scenarios. To evaluate algorithm performance under such scenario, we construct the index using 3 uniformly distributed attributes and apply filtering conditions on all 3 attributes simultaneously during the query process.

@@

\begin{figure*}[t]
	\centering

	% 1. 全局图例 (Legend) - 位置保持不变
	\includegraphics[width=0.9\textwidth]{figures/exp/attribute_legend.pdf}

	% --- 主要改动：将以下三个 subfigure 全部放在同一行 ---

	% 2. 第一部分：两张图，共用标题
	% [b]表示按底部对齐，在一行内通常比顶部对齐[t]效果好
	% 宽度从\textwidth缩小到0.32\textwidth
	\begin{subfigure}[b]{0.39\textwidth}
		\centering
		% 内部图片宽度使用\linewidth，它会自适应为容器宽度(0.32\textwidth)
		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_multimodel.pdf}
		\hfill 
		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_multimodel_1.pdf}
		\caption{MultiModal}
		\label{fig:attribute-multimodal} 
	\end{subfigure}
	\hfill % 在第一部分和第二部分之间添加弹性间距
	% 3. 第二部分：两张图，共用标题
	\begin{subfigure}[b]{0.39\textwidth}
		\centering
		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_85.pdf}
		\hfill
		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_71.pdf}
		\caption{Cross-Platform}
		\label{fig:attribute-cross-platform}
	\end{subfigure}
	\hfill % 在第二部分和第三部分之间添加弹性间距
	% 4. 第三部分：只有一张图
	\begin{subfigure}[b]{0.203\textwidth}
		\centering
		% !!! 注意：这是一个占位符，请替换成您自己的第五张图 !!!
		\includegraphics[width=0.96\linewidth]{figures/exp/attribute_100M.pdf} 
		\caption{Dig Dataset}
		\label{fig:attribute big dataset}
	\end{subfigure}

	% 5. 全局总标题
	\caption{\textcolor{violet}TrinityExtension——Attribution}
	\label{fig:TrinityExtension——Attribution_main}
\end{figure*}

@@

	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}} 
	\textcolor{cyan}{To investigate the impact of different server configurations on the performance of the algorithms, we conducted additional experiments on Server B using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}. Compared with the experimental results on Server A shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}f, the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations. Due to the lower CPU frequency and smaller RAM capacity of Server B compared to Server A, the QPS values are slightly lower across all methods.}
%	\textcolor{red}{To investigate the impact of different server configurations on the performance of the algorithms, we conducted additional experiments on a server equipped with two Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}. Compared with the experimental results on the original server (as shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}(f)), the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations. Due to the lower CPU frequency of the Xeon 6330 compared to the original server, the QPS values are slightly lower across all methods.}

@@

% 使用 figure* 环境来实现图片横跨双栏
% 使用 figure* 环境来实现图片横跨双栏

@@

\begin{figure*}[t]
	\centering

	% 1. 全局图例 (Legend) - 位置保持不变
	\includegraphics[width=0.9\textwidth]{figures/exp/range_legend.pdf}

	% --- 主要改动：将以下三个 subfigure 全部放在同一行 ---

	% 2. 第一部分：两张图，共用标题
	% [b]表示按底部对齐，在一行内通常比顶部对齐[t]效果好
	% 宽度从\textwidth缩小到0.32\textwidth
	\begin{subfigure}[b]{0.39\textwidth}
		\centering
		% 内部图片宽度使用\linewidth，它会自适应为容器宽度(0.32\textwidth)
		\includegraphics[width=0.495\linewidth]{figures/exp/range_multimodel.pdf}
		\hfill 
		\includegraphics[width=0.47\linewidth]{figures/exp/range_multimodel_1.pdf}
		\caption{MultiModal}
		\label{fig:range-multimodal} 
	\end{subfigure}
	\hfill % 在第一部分和第二部分之间添加弹性间距
	% 3. 第二部分：两张图，共用标题
	\begin{subfigure}[b]{0.39\textwidth}
		\centering
		\includegraphics[width=0.495\linewidth]{figures/exp/range_85.pdf}
		\hfill
		\includegraphics[width=0.47\linewidth]{figures/exp/range_71.pdf}
		\caption{Cross-Platform}
		\label{fig:range-cross-platform}
	\end{subfigure}
	\hfill % 在第二部分和第三部分之间添加弹性间距
	% 4. 第三部分：只有一张图
	\begin{subfigure}[b]{0.203\textwidth}
		\centering
		% !!! 注意：这是一个占位符，请替换成您自己的第五张图 !!!
		\includegraphics[width=0.96\linewidth]{figures/exp/range_deep100M.pdf} 
		\caption{Dig Dataset}
		\label{fig: range big dataset}
	\end{subfigure}

	% 5. 全局总标题
	\caption{\textcolor{violet}TrinityExtension——Range}
	\label{fig:TrinityExtension——Attribution_main}
\end{figure*}

	%Similar to the evaluation of \textit{Attribute Filtering} algorithms, 
	Similarly, we also evaluate \textcolor{orange}{4} key metrics mentioned above in \textit{Range Filtering} algorithms. \textcolor{orange}{For the YT-Audio dataset with synthetic attributes and the YT-Audio dataset with real attributes, we can found that the data for index construction is basically the same, indicating that the authenticity of the attribute has almost no effect on index construction.
	However, the WIT dataset with synthetic labels is 2048-dimensional, while the WIT-Real dataset with real labels is 512-dimensional, so the dimension will cause a big difference.}

@@

	\textit{\textbf{Index size.}} 
	As shown in Figure~\ref{fig:rangeFilter_index_size_mb}, Among all algorithms, Faiss has the smallest index size. Because IVF only adds centroid data and partition information to the vector dataset, the IVF index is only slightly larger than the vector dataset.
	On low-dimensional datasets (Deep, YT-Audio), PASE requires the most storage. Its implementation likely wastes space due to alignment padding and inefficient encoding. %(e.g., Base64).

	SeRF maintains a compact index for low-dimensional data. However, for high-dimensional dataset (WIT), SeRF stores more edges and dynamic range data, significantly increasing its size.

	\textit{\textbf{Build peak memory.}}
	As Figure~\ref{fig:rangeFilter_build_memory_mb} shows, Faiss uses the least memory on low-dimensional datasets. It stores minimal temporary data during index construction.

	On low-dimensional datasets, DSG and WinFilter exhibit higher peak memory usage compared to other algorithms. This suggests that their index structures suffer from severe structural redundancy and are difficult to compress in low-dimensional scenarios.
	%因为低维空间中数据点之间的欧氏距离普遍较小，点与点之间更易互为近邻，从而导致图索引中产生大量冗余的边连接。

	%As Figure~\ref{fig:rangeFilter_memory_mb} shows, Faiss uses the least memory on low-dimensional datasets (Deep, YT-Audio). It stores minimal temporary data (e.g., vectors, centroids, distances) during index construction.

	For high-dimensional dataset WIT, iRange achieves the lowest peak memory usage. It pre-builds graphs only for a limited number of intervals, avoiding explicit index construction for all possible query ranges. Its index structure remains stable in high dimensions without significant graph growth. This effectively controls index size, making iRange more advantageous for high-dimensional datasets.
	In contrast, \textcolor{orange}{Milvus exhibits the highest memory consumption,}
	%Unify exhibits the highest memory consumption, indicating that its index construction process is highly sensitive to the dimensionality of the data.

		\textit{\textbf{\textcolor{orange}{Search peak memory.}}}

	%	\textcolor{orange}{As shown in Figure~\ref{fig:rangeFilter_search_memory_mb}, Faiss and Milvus have the lowest peak memory usage during search. Similar to attribute filtering, Faiss also has a smaller index size and no other additional memory usage, so the peak memory usage in range queries is slightly higher than the index size. Milvus reason:. WinFilter achieves the highest peak memory usage on almost all datasets. The reason is:. For the high-dimensional dataset WIT, UNIFY occupies the highest peak memory. The reason is:.}

		\textcolor{orange}{As for the search peak memory usage, we can find from the Figure ~\ref{fig:rangeFilter_search_memory_mb} that it is basically consistent with the build peak memory usage trend. The algorithm needs to load the complete index into memory during search. Therefore, algorithms with high building overhead, such as WinFilter, also have high search overhead; algorithms with low building overhead, such as Faiss, also have low search overhead. For Milvus, search does not require full index loading and there is additional metadata overhead when building, so the performance is different from the trend.}

@@

	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}}
	\textcolor{cyan}{As described in Section 4.2.4, we performed additional range filtering experiments using the YT-Audio-Real dataset on Server B, with results presented in Figure~\ref{fig:Different_Computer_range}. When compared with the experimental results of Server A shown in Figure~\ref{fig:exp_8_2}a, our findings remain consistent with those reported in Section 4.2.4. For brevity and due to space limitations, we omit further discussion of these redundant results.}
%	\textcolor{cyan}{Consistent with Section 4.2.4, we conducted additional range filtering experiments using the YT-Audio-Real dataset on the same server, with results shown in Figure \ref{fig:Different Computer range}. Compared with the original server's experimental results (Figure \ref{fig:exp_8_2}($e$)), the conclusions remain identical to those described in Section 4.2.4. Due to space constraints, these details are not reiterated here.}

@@

\begin{table*}[htbp]
	\caption{Algorithm Recommendation}
	\resizebox{\textwidth}{!}{
		\begin{tabular}{|l|*{16}{c|}}
			\hline
			\multirow{2}{*}{\textbf{Application Scenarios / Algorithms}} 
			& \multicolumn{6}{c|}{\textbf{AF}} 
			& \multicolumn{5}{c|}{\textbf{RF}} 
			& \multicolumn{5}{c|}{\textbf{AF / RF}} \\
			\cline{2-17}
			& \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS}  & \textbf{UNG} & \textbf{Puck} 
			& \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{Win} 
			& \textbf{ACORN}& \textbf{Faiss} & \textbf{Milvus} & \textbf{VBASE} & \textbf{PASE} \\
			\hline
			\textbf{Query Performance} & H & M & H & M &\textbf{ H} & H & M & M & L & M & H & M/M & M/M & M/M & L/L & L/L \\
			\textbf{Index Time} &M  &M  &M  &M  &M  &H  &L  &M  &H  &L  &L  &L/L &\textbf{H}/ \textbf{H} &M/H  &M/M  &L/L  \\
			\textbf{Peak Memory} &L  &M  &M  &M  &M  &H  &L  &L  &M  &L  &L  &L/L  &\textbf{H}/\textbf{H}  &M/M  &H/M  &H/H \\

			\textbf{Large-Scale Dataset} & H & H & L & L &\textbf{H } &H  &M  &H  &M  &H  &\textbf{H}  &M/L  &L/M  &L/L  &M/M  &-  \\
			\textbf{Rare Attribute \& Low Range} &M  &M  &H  &H &\textbf{H}  &H  &H  &H  &L  &M  &\textbf{H} &M/M  &M/M  &L/L  &L/L  &L/L  \\
			\textbf{Robust to MultiModal Dataset} &H  &H  &L  &H  &H  &L  &M  &H  &M  &H  &H  &H/H  &M/M  &L/L  &L/L  &-/-  \\
			\textbf{Robust to Attribute Distribution} &L  &L  &H  &H  &H  &H  &-  &-  &-  &-  &-  &H/-  &L/-  &H/-  &L/-  &L/-  \\
			\textbf{High LID Dataset} &  &  &  &  &  &  &  &  &  &  &  &  &M  &L  &L/  &L/  \\
			\textbf{General-Purpose} &\faCheck  &\faCheck  &\faTimes  &\faTimes  &\faCheck  &\faTimes  &\faTimes  &\faCheck &\faTimes  & \faTimes &\faCheck&\faTimes  &\faCheck  &\faCheck  &\faTimes &\faTimes  \\
			\hline
		\end{tabular}
	}
	\centering
\end{table*}
